Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of neutron star - black hole binary observations

### 2016-10-17 Paper/paper.tex
insert 1d figures for param biases in paper
finalizing figures

\includegraphics[width=1.6\columnwidth]{plots/TNMchirpBiasesOverCIWidths_CI90_0_Lambda_SNR30_70_linear}
\includegraphics[width=0.8\columnwidth]{plots/TNMchirpBiasesOverCIWidthsVsSNR_Lambda500_CI90_0}
% \includegraphics[width=0.67\columnwidth]{plots/TNMchirpBiasesOverCIWidthsVsSNR_Lambda800_CI90_0}
\includegraphics[width=0.8\columnwidth]{plots/TNMchirpBiasesOverCIWidthsVsSNR_Lambda1000_CI90_0}\\
\includegraphics[width=0.8\columnwidth]{plots/TNMchirpBiasesOverCIWidthsVsSNR_Lambda1500_CI90_0}
\includegraphics[width=0.8\columnwidth]{plots/TNMchirpBiasesOverCIWidthsVsSNR_Lambda2000_CI90_0}

@@

\includegraphics[width=2\columnwidth]{plots/TNEtaBiasesOverCIWidths_CI90_0_Lambda_SNR20_70_linear}

@@

% \includegraphics[width=\columnwidth]{plots/TNChiBHBiasesOverCIWidthsVsSNR_All_CI68_3.pdf}
% \includegraphics[width=\columnwidth]{plots/TNChiBHBiasesOverCIWidthsVsSNR_All_CI90_0.pdf}

@@

\includegraphics[trim={2cm 0 0 0},width=2.2\columnwidth]{plots/TTLambdaRawCIWidths90_0_Lambda_SNR}

>>>>

\includegraphics[width=1.95\columnwidth]{plots/TNMchirpBiasesOverCIWidths_CI90_0_Lambda_SNR30_70_linear}
% \includegraphics[width=0.8\columnwidth]{plots/TNMchirpBiasesOverCIWidthsVsSNR_Lambda500_CI90_0}
% % \includegraphics[width=0.67\columnwidth]{plots/TNMchirpBiasesOverCIWidthsVsSNR_Lambda800_CI90_0}
% \includegraphics[width=0.8\columnwidth]{plots/TNMchirpBiasesOverCIWidthsVsSNR_Lambda1000_CI90_0}\\
% \includegraphics[width=0.8\columnwidth]{plots/TNMchirpBiasesOverCIWidthsVsSNR_Lambda1500_CI90_0}
% \includegraphics[width=0.8\columnwidth]{plots/TNMchirpBiasesOverCIWidthsVsSNR_Lambda2000_CI90_0}

@@

\includegraphics[width=1.95\columnwidth]{plots/TNEtaBiasesOverCIWidths_CI90_0_Lambda_SNR20_50_linear}
% \includegraphics[width=0.8\columnwidth]{plots/TNEtaBiasesOverCIWidthsVsSNR_Lambda500_CI90_0}
% % \includegraphics[width=0.67\columnwidth]{plots/TNEtaBiasesOverCIWidthsVsSNR_Lambda800_CI90_0}
% \includegraphics[width=0.8\columnwidth]{plots/TNEtaBiasesOverCIWidthsVsSNR_Lambda1000_CI90_0}\\
% \includegraphics[width=0.8\columnwidth]{plots/TNEtaBiasesOverCIWidthsVsSNR_Lambda1500_CI90_0}
% \includegraphics[width=0.8\columnwidth]{plots/TNEtaBiasesOverCIWidthsVsSNR_Lambda2000_CI90_0}

@@

% % \includegraphics[width=\columnwidth]{plots/TNChiBHBiasesOverCIWidthsVsSNR_All_CI68_3.pdf}
% % \includegraphics[width=\columnwidth]{plots/TNChiBHBiasesOverCIWidthsVsSNR_All_CI90_0.pdf}
% \includegraphics[width=0.8\columnwidth]{plots/TNChiBHBiasesOverCIWidthsVsSNR_Lambda500_CI90_0}
% % \includegraphics[width=0.67\columnwidth]{plots/TNChiBHBiasesOverCIWidthsVsSNR_Lambda800_CI90_0}
% \includegraphics[width=0.8\columnwidth]{plots/TNChiBHBiasesOverCIWidthsVsSNR_Lambda1000_CI90_0}\\
% \includegraphics[width=0.8\columnwidth]{plots/TNChiBHBiasesOverCIWidthsVsSNR_Lambda1500_CI90_0}
% \includegraphics[width=0.8\columnwidth]{plots/TNChiBHBiasesOverCIWidthsVsSNR_Lambda2000_CI90_0}

@@

\includegraphics[trim={3cm 0 0 0.5cm},width=2.2\columnwidth]{plots/TTLambdaRawCIWidths90_0_Lambda_SNR}
